On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-02-03 docs/mvfits_paper/referee_reports_and_responses/Response_Ref1.txt

8. (p. 1, L52-53) Thank you. We hope that the current text will avoid any confusion.

9. (p. 2, L30) Thank you. We hope that the current text will avoid any confusion.

10. (p. 2, L30) Thank you. We agree that Yang+ should be referenced here.

11. (p. 2, L39) Thank you. We have updated this section to avoid any confusion.

12. (In Eq.6) Thank you. We have clarified the notation.

13. (p. 2, L26-27) Thank you for mentioning the Stone-Weierstrass theorem. We do not wish to reference this theorem in place of the series expansion as the latter is more accessible to a physics audience. We note that our introduction to the discussion is generally applicable given some smooth functoin and an epsilon neighborhood around a point. We intend primarily to motivate a general numtinobial basis perspective of our algorithms from first principles. he text has been modified in an effort to clarify this intention.

14. (Algs. 2 and 5 ...) Thank you. We have clarified that we refer to the set of all multinomial combinations of basis vectors up to a predefined maximum order.

15. (Algs. 2 and 5 ...) Thank you. We have corrected these lines to reference epsilons.

16. (p. 3, L60) The current description of \lambda_{bulk} seeks to communicate the presense of the constant term.

17. (p. 5, L3-4) We refer the reviewer to the introducion section here: https://en.wikipedia.org/wiki/Runge%27s_phenomenon. We have sought to clarify the text to minimize confusion.

18. ( Eq. 20 ) We refer the referee to Eq 21

19. Via Eq. 15, n>=1 for alpha. Here, "implicitely" n plays no real role in the algorithm and therefore need not be stored and increamented.

20. (Alg. 4, step 4) Thank you. We have defined var to be the variance.

21. (Alg. 4, step 4) Thank you. Yes.

22. (p. 8, final line) We have clarified the text.

23. (Fig. 4) We have clarified the text.

24. Code: While we are appreciative of the referee's comments, we point out to the submitted draft only pertains to the GMVP and GMVR algorithms.

### 2019-02-03 docs/mvfits_paper/mvf.tex
more additions to ref report 2 --- the ref is a bellend

\cite{ Hannam:2013oca, London:2017bcn, Khan:2015jqa, Schmidt:2014iyl, Mehta:2017jpq, Khan:2018fmp }.

@@

Here, we present the first models for $\cw\lmn$ that explicitly account for zero-damping \textit{and} non-zero-damping in the extremal Kerr limit.

@@

% \par For the modeling of $\sigma\LMlmn$, we note that the results presented in \cite{Berti:2014fga} are limited to cases where the azimuthal indices, $\ell$ and $\bar{\ell}$, are less than or equal to 3.
% As the most advanced signal models include at least $\ell$ or $\bar{\ell}$ of 3, there is use in extending current results.
% In particular, it is well known that $\sigma_{43330}$ can have a significant impact on the $(4,3)$ spherical multipole (via \ceqn{hlm}).
% For consistency with the multipolar content of current ringdown models, we extend previous results to include the most significant multipoles with $\ell \leq 5$ \cite{London:2018gaq,London:2014cma}.

@@

In addition to our

@@

In \sec{discuss}, we review the performance of \gmvp{} and \gmvr{}, and we discuss current and potential applications for these methods.

@@

@@

  \caption{A positive (forward) greedy algorithm, \pgreedy{}. Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error (e.g. L2 norm). In this setting, $\mathcal{A}$ is assumed to have access to peripheral information, such as the training data.}

@@

given training data thought to be related to a smooth multivariate function, it may in many cases be well approximated by a truncated series expansion in an appropriate coordinate basis.

@@

    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product (i.e. tensor product) of the power set of each basis symbol

@@

      \If { $|\mlam^{(d)}_{opt}-\mlam^{(d-1)}_{opt}|<tol$ }

@@

Worst, in cases where the underlying dataset is best described by a rational function, no polynomial order will yield satisfactory results (i.e. the well known ``Runge's phenomenon'' \cite{10.2307/2323093}).

@@

\par Of the simplest examples are rational functions of the form

@@

	\caption{ Standard summary plot for Greedy Multivariate Rational fitting algorithm (\gmvr) as implemented in \cite{lionel_london_2018_1402516}. (\textit{left}) 3D plot of training data (black dots) and final fit (red mesh). (\textit{center top}) Same as left most panel, but in index space. (\textit{center bottom}) {Percent residual error with respect to validation data (grey blocks) along with uniform (black) and gaussian (red) fits to error. The validation data were generated in the same manner as the training data.} (\textit{top right}) convergence of the L2 norm during iterative refinement. (\textit{bottom right}) Same as top right, but on log scale, where $\epsilon_0$ is the value of $\epsilon$ at the final $k^{\mathrm{th}}$ iteration of refinement. }

@@

\par However, we note that $\hat{P}$ depends on $g$ signals.

@@

The refinement process is to terminate when a measure of model error (e.g. $||g^{(0)}-g^{(n)}||$) passes a predetermined threshold.

@@

    \State Calculate the model representation error, e.g.: $\epsilon = ||\hatU \vecmu - \vec{f}||/||\vec{f}||$, where $||a||$ is the L-2 norm of $a$.

@@

    \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = ||var(g^{(n)} - g^{(0)})||/||g^{(0)}||$.

@@

      \State $done = \epsilon^{(n-1)}-\epsilon^{(n)} < tol$

@@

This is equally true in cases where $(\bar\ell,\bar{m}) \neq (\ell,m)$.

@@

    \State Define, $\mlam_{bulk}$, the bulk symbol space using the tensor-product of the power set of each basis symbol. This is the combined bulk for numerator and denominator symbols.

>>>>

\cite{Hannam:2013oca, London:2017bcn, Khan:2015jqa, Schmidt:2014iyl, Mehta:2017jpq,Khan:2018fmp}.

@@

Like Ref.~\cite{Cook:2014cta}, we present models for $\cw\lmn$ that explicitly account for zero-damping in the extremal Kerr limit.

@@

We go further by presenting models that also account for non-zero-damping in modes such as $(\ell,m,n)=(2,1,0)$ and $(3,2,0)$.

@@

Here these \qnm{} are explicitly modeled on a continuation of the positive spin line to negative spin.

@@

Quantitative comparisons are made between our models and those presented in Refs.~\cite{Berti:2005ys, Berti:2014fga}.
In \sec{discuss}, we review the effectiveness of \gmvp{} and \gmvr{}, and we discuss current and potential applications for these methods.

@@

Here ``$*$'' denotes the conjugate transpose.

@@

  \caption{A positive (forward) greedy algorithm, \pgreedy{}. Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error (e.g. $L^2$ norm). In this setting, $\mathcal{A}$ is assumed to have access to peripheral information, such as the training data.}

@@

given training data thought to be related to a smooth multivariate function, it may, particularly on small scales, be well approximated by a truncated series expansion in an appropriate coordinate basis.

@@

    \State Define, $\mlam_{bulk}$, the bulk symbol space, to be the set of all multinomial combinations of basis vectors up to a predefined maximum order.

@@

      \If { $|\epsilon^{(d)}_{opt}-\epsilon^{(d-1)}_{opt}|<tol$ }

@@

Worst, in cases where the underlying dataset is best described by a rational function, no polynomial of the same family describing the numerator and denominator will yield satisfactory results (e.g. the well known ``Runge's phenomenon'' \cite{10.2307/2323093}).

@@

In general, the optimal polynomial basis may not be clear, and so a more general set of ansatzes may be of use.
\par Of the simplest of such ansatzes are rational functions of the form

@@

	\caption{ Standard summary plot for Greedy Multivariate Rational fitting algorithm (\gmvr) as implemented in \cite{lionel_london_2018_1402516}. (\textit{left}) 3D plot of training data (black dots) and final fit (red mesh). (\textit{center top}) Same as left most panel, but in index space. (\textit{center bottom}) {Percent residual error with respect to validation data (grey blocks) along with uniform (black) and gaussian (red) fits to error. The validation data were generated in the same manner as the training data.} (\textit{top right}) convergence of the $L^2$ norm during iterative refinement. (\textit{bottom right}) Same as top right, but on log scale, where $\epsilon_0$ is the value of $\epsilon$ at the final $k^{\mathrm{th}}$ iteration of refinement. }

@@

\par However, we note that $\hat{P}$'s depends on $g$.

@@

The refinement process is to terminate when a measure of model error (e.g. the $L^2$ norm $||g^{(0)}-g^{(n)}||$) passes a predetermined threshold.

@@

    \State Calculate the model representation error, e.g.: $\epsilon = ||\hatU \vecmu - \vec{f}||/||\vec{f}||$, where $||a||$ is the $L^2$ norm of $a$.

@@

    \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = ||var(g^{(n)} - g^{(0)})||/||g^{(0)}||$, where $var$ is the variance.

@@

      \State $done = |\epsilon^{(n-1)}-\epsilon^{(n)}| < tol$

@@

Consistency with the Schwarzschild limit is equally true in cases where $(\bar\ell,\bar{m}) \neq (\ell,m)$.

@@

    \State Define, $\mlam_{bulk}$, the bulk symbol space, to be the set of all multinomial combinations of basis vectors up to a predefined maximum order. This is the combined symbol space for numerator and denominator symbols.
